% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{verbatim}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.


% Set your name here
\def\name{Yuan Liao}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets

\begin{document}

% Place name at left
\begin{center}

 {\huge   Yuan Liao}



\end{center}



\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
  \end{center}



% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}


\begin{minipage}{0.45\linewidth}

Tippie College of Business\\
University  of Iowa\\
W308 John Pappajohn Business Building\\
Iowa City, IA 52242
\end{minipage}
\begin{minipage}{0.45\linewidth}
%Phone (847) 219-7584\\
\href{http://myweb.uiowa.edu/yliao13}{http://myweb.uiowa.edu/yliao13} \\
%\href{https://scholar.google.com/citations?user=bffdsMgAAAAJ&hl=en&oi=ao}{Google scholar: Yuan Liao} \\
Email: \href{yuan-liao@uiowa.edu}{yuan-liao@uiowa.edu}
 

\end{minipage}



\section*{EMPLOYMENT}
\hrule

\hfill

\begin{itemize}

\item \textbf{Tippie Children Professor}, August 2025- \\
University of Iowa, Tippie College of Business
\item \textbf{Professor}, July 2022- 2025\\
Rutgers University, Department of Economics
\item \textbf{Associate Professor}, July 2016-2022\\
Rutgers University, Department of Economics
\item \textbf{Assistant Professor}, July 2012- 2016\\
University of Maryland at College Park, Department of Mathematics

%\begin{itemize}
%\item Research area: High dimensional sparse modeling
%\item Advisor:  Jianqing Fan
%\end{itemize}
\end{itemize}


\section*{VISTING POSITIONS}
\hrule

\hfill

\begin{itemize}
\item \textbf{Visiting Associate Professor}, Fall 2019\\
 University of Pennsylvania, Department of Economics


\item\textbf{Visiting Assistant Professor}, Fall 2015\\
Princeton University, Department of Operations Research and
Financial Engineering%\\ (advised by Jianqing Fan)
%\begin{itemize}
%\item Research area: High dimensional sparse modeling
%\item Advisor:  Jianqing Fan
%\end{itemize}
\end{itemize}



\section*{EDUCATION}
\hrule

\hfill
\begin{itemize}
\item \textbf{Postdoctoral Research Associate}, July 2010-Aug 2012\\
Princeton University, Department of Operations Research and
Financial Engineering%\\ (advised by Jianqing Fan)
  \item \textbf{Ph.D. in Statistics}, 2010, Northwestern University, Evanston, IL
  \begin{itemize}
\item Dissertation:  Bayesian Analysis in Partially Identified Parametric and Nonparametric Models
\item  Committee members:  Wenxin Jiang,  Joel Horowitz, Thomas  Severini,  Elie Tamer
%\item Three publications based on  dissertation:  \textit{Ann.Statist.} \textbf{38} 275-316,
\end{itemize}
   \item \textbf{B.S. in Mathematics}, 2005, Tsinghua University, Beijing
\end{itemize}



\section*{EXPERTISE}
\hrule

\hfill




Asset Pricing, Machine Learning, Econometrics


 


\section*{PUBLICATIONS}
\hrule
\hfill

 %\textbf{Peer-Reviewed}
 
 
 \medskip
 
  
  
  \begin{enumerate}
  
  %\item      {\textsc{Liao, Y.}} , \textsc{Ma, X.}, \textsc{Neuhierl, A.}   and  \textsc{Shi, Z..} (2024)   Does noise hurt economic forecasts?     under review  		
%   \item    \textsc{Fan, J.}, \textsc{Ke, Z,},   {\textsc{Liao, Y.}} ,  and \textsc{Neuhierl, A.}  (2024)   Structural  deep learning in conditional asset pricing.     {\it  {Journal of Finance}.   } revised and resubmitted
   




  \item  \textsc{Choi, J.}   \textsc{\textsc{Kwon, H.}}, and \textsc{Liao, Y.}   (2025)  Inference for low-rank completion without estimating the rank.    {\it  { Journal of American Statistical Association}   },    forthcoming 

 
   \item   \textsc{\textsc{Liao, Y.}} and  \textsc{Todorov, V.} (2024)  Changes in the Span of Systematic Risk Exposures.     {\it  { Quantitative Economics}   }, 15,    817–847
		

	



  \item  \textsc{Choi, J.}   \textsc{\textsc{Kwon, H.}}, and \textsc{Liao, Y.}   (2024)  Inference for low-rank completion without sample splitting with application to treatment effect estimation     {\it  { Journal of Econometrics}   },   240, 105682
	
	


	
  \item  \textsc{Chen, X. }   \textsc{\textsc{Liao, Y.}} and  \textsc{Wang, W.} (2024)  Inference on time series nonparametric conditional moment
		restrictions using general sieves.     {\it  { Journal of Econometrics}   },   conditionally accepted 
		
		

		
		
		
		

  \item  \textsc{Lee, S., }   \textsc{\textsc{Liao, Y.}}, \textsc{Seo, M.} and \textsc{Shin, Y.} (2024)  Fast inference for quantile regression with tens of millions of observations   {\it  { Journal of Econometrics}   },   forthcoming 






 

\item   \textsc{Bai, J.},   \textsc{Choi, S.} and \textsc{\textsc{Liao, Y.}}  (2024) Standard errors for panel data models with unknown clusters    {\it  { Journal of Econometrics},    } 240, 

	
\item  \textsc{Chernozhukov, V., Hansen, C., Liao, Y.}  and  \textsc{\textsc{Zhu, Y.}} (2023) Inference for low rank models {\it  { Annals of Statistics},  }    {51}, 1309- 1330.


 
\item  \textsc{Lee, S., }   \textsc{\textsc{Liao, Y.}}, \textsc{Seo, M.} and \textsc{Shin, Y.} (2022)  Fast and robust online inference with stochastic gradient descent via random scaling.  {\it  {AAAI Conference on Artificial Intelligence    }   } vol 36,  7381-7389. 




\item  \textsc{Chen, X., }  \textsc{Lee, S., }   \textsc{\textsc{Liao, Y.}}, \textsc{Seo, M.} and \textsc{Shin, Y.} (2022)  SGMM: Stochastic Approximation to Generalized Method of Moments  {\it Journal of Financial Econometrics   } forthcoming


 
      
   
  \item  \textsc{Lee, S., }   \textsc{\textsc{Liao, Y.}}, \textsc{Seo, M.} and \textsc{Shin, Y.} (2021)  	Factor driven two regime regression. {\it  Annals of Statistics}, vol 49, 1656--1678



 
  \item  \textsc{Lee, S., }   \textsc{\textsc{Liao, Y.}}, \textsc{Seo, M.} and \textsc{Shin, Y.} (2021)  Sparse HP filter: finding kinks in the COVID-19 contact rate.     {\it  { Journal of Econometrics}   }, vol 220,  158-180

 
 
 
  \item    \textsc{Fan, J.,   \textsc{Ke, Y.} and \textsc{Liao, Y.}}  (2021)  Augmented factor models with applications to validating market risk factors and forecasting bond risk premia.  {\it  { Journal of Econometrics},    } 222, 269--294

    \item  \textsc{Giglio, S.}   \textsc{\textsc{Liao, Y.}} and   \textsc{Xiu, D.} (2021)  	Thousands of alpha tests. {\it   Review of Financial Studies}, 3456--3496.
 
 
 		   

 \item  \textsc{Fan, J.} and    \textsc{\textsc{Liao, Y.}}  (2021)  	 Learning latent factors from diversified projections and its applications to over-estimated and weak factors. {\it   Journal of the American Statistical Association}, vol 117, 909-924





\item     \textsc{\textsc{Liao, Y.}} and \textsc{Simon, A.} (2019)  Bayesian inference for smooth partially identified convex models.  {\it  {Journal of Econometrics},}  211, 338-360
 







\item     \textsc{Lee, S., \textsc{Liao, Y.}, Seo, M.} and \textsc{Shin, Y.} (2018)  Oracle estimation of a change point in high dimensional quantile regression.  {\it  {Journal of the American Statistical Association},}  { 113}, 1184-1194. 
 

  \item   \textsc{Hansen, C.}  and \textsc{\textsc{Liao, Y.}}  (2018) The factor lasso for high dimensional inference in economic applications.   {\it  { Econometric Theory},     } 1-45.
 
 
  \item   \textsc{Bai, J.}  and \textsc{\textsc{Liao, Y.}}  (2017) Inferences in panel data with interactive effects using large covariance matrices    {\it  { Journal of Econometrics},    }
 {200}, 59-78.


\item  \textsc{Chernozhukov, V., Hansen, C.}  and \textsc{\textsc{Liao, Y.}} (2017)  A Lava attack for the recovery of sums of sparse and dense signals.  {\it  { Annals of Statistics},  }    {45}, 39-76.



  \item   \textsc{Bai, J.}  and \textsc{\textsc{Liao, Y.}}  (2016) Efficient estimation of approximate factor models via regularized maximum likelihoods.      {\it  { Journal of Econometrics},    }
 {191}, 1-18.




\item   \textsc{Fan, J.} and \textsc{\textsc{Liao, Y.}} (2014) Endogeneity in high dimensions. {\it  { Annals of Statistics},  }    {42}, 872-917.

\item    \textsc{Fan, J., \textsc{Liao, Y.}} and \textsc{Mincheva, M.}(2013)  Large covariance estimation by thresholding principal orthogonal complements.    {\it  { Journal of the Royal Statistical  Society  Series  B} (\textit{\textbf{with discussion}}),  }    \textbf{75}, 603-680\\
Reviewed by 7 screeners, 5 referees and 1 post-refereeing screener,  read before Royal Statistical Society on 13 February 2013.

		

\item   \textsc{Fan, J., \textsc{Liao, Y.}} and \textsc{Mincheva, M.}(2011) High dimensional  covariance matrix estimation in approximate factor models. {\it  { Annals of Statistics}, }    {39}, 3320-3356.


  \item    \textsc{Fan, J., \textsc{Liao, Y.}} and \textsc{Wang, W.}(2016) Projected principal components analysis in factor models.  {\it  { Annals of Statistics},}    {44}, 219-254.
 
 

  \item    \textsc{Fan, J., \textsc{Liao, Y.}} and \textsc{Shi, X.}(2015) Risks of large portfolios.  {\it  { Journal of Econometrics},    }   {186}, 367-387.

 

 \item    \textsc{Fan, J., \textsc{Liao, Y.}} and \textsc{Yao, J.}(2015) Power enhancement in high-dimensional cross sectional tests. {\it    {Econometrica},  }   {83}, 1497-1541.









	





 %\item  \textsc{Chernozhukov, V., Hansen, C.}  and \textsc{\textsc{Liao, Y.}} (2015)  A Lava attack for the recovery of sums of sparse and dense signals.   {\it \textbf{ Annals of Statistics},  accepted for publication }





  \item \textsc{\textsc{Liao, Y.}} and \textsc{W. Jiang} (2011) Posterior consistency of nonparametric conditional moment restricted models.  {\it  { Annals of Statistics},   }    {39}, 3003-3031.

\item \textsc{\textsc{Liao, Y.}} and \textsc{W. Jiang} (2010) Bayesian analysis in moment inequality models.\\
{\it  {Annals of Statistics}}. {38}, 275-316.




\end{enumerate}





 %\textbf{Under Review}
 %\begin{enumerate}

 
%\item  \textsc{Lee, S., }   \textsc{\textsc{Liao, Y.}}, \textsc{Seo, M.} and \textsc{Shin, Y.} (2021) Fast and robust online inference using random scaling.  {\it submitted}.



%  \item   \textsc{Chernozhukov, V., Hansen, C.}   \textsc{\textsc{Liao, Y.}} and   \textsc{Zhu, Y.} (2020)  Inference for low rank models.   {\it submitted}.

 


% \item   \textsc{\textsc{Liao, Y.}} and   \textsc{Yang, X.} (2019)   Uniform inference for characteristic effects of large continuous time linear models.  {\it submitted}



 
 

%\end{enumerate}

 \textbf{Book Chapters and Overviews}

  \begin{enumerate}
%   \setcounter{enumi}{27} 
  \item    \textsc{Fan, J.}, \textsc{Li, K.} and \textsc{Liao, Y.},   (2021)  Recent developments on factor models and its applications on econometric learning.  \textit{ Annual Reviews of Financial Economics.} vol. 13, 401-430






\item    \textsc{Lee, S., \textsc{Liao, Y.}, Seo, M.} and \textsc{Shin, Y.} (2020)  Desperate times call for desperate measures: government spending multipliers in hard times.   \textit{ Economic Inquiry} 

    \item   \textsc{Fan, J.},  \textsc{\textsc{Liao, Y.}} and \textsc{Liu, H.}  (2016) An overview on the estimation of large covariance and precision matrix estimation.    \textit{  { The Econometrics Journal}}  {19}, C1-C32.

  \item   \textsc{Fan, J.},  \textsc{\textsc{Liao, Y.}} and \textsc{Liu, H.}  (2015) Approaches to high-dimensional covariance and precision matrix estimation.   in
    {\it Financial Signal Processing and Machine Learning}, edited by A.N. Akansu, S.R. Kulkarni, D. Malioutov, I. Pollak.  Wiley

     \item   \textsc{Bai, J.},  \textsc{\textsc{Liao, Y.}} and \textsc{Yang, J.}  (2014) Unbalanced panel data models with interactive effects.  in {\it The Oxford Handbook of Panel Data}, chapter 5, edited by Badi Baltagi.



\end{enumerate}



%\textbf{Work in Progress}

%\begin{enumerate}

 %  \item



%\end{enumerate}




\section*{FELLOWSHIPS AND HONORS}
\hrule
\hfill
\begin{itemize}
 
 
  \item Henry B. Tippie Research Fellow (University of Iowa 2025)
 
 \item Fellow of Journal of Econometrics (elected in 2024)
 
\item ICCM Best Paper Award (distinguished), 2018  (for the paper Fan, Liao and Mincheva 2013)
 
\item  Research (Council) and Scholarship  Award (Maryland, 2015),  (Rutgers 2017)
\item US Junior Oberwolfach Fellow, 2013
\item Journal of the Royal Statistical Society-B read paper, 2013
\item IMS New Researchers Conference, 2013

\item Dissertation Year Fellowship, Northwestern University, 2010

%\item Conference Travel Grant, Northwestern University, 2009, 2010
%  \item Graduate School Fellowship, Northwestern University, 2005
\end{itemize}


\section*{ PRESENTATIONS}
\hrule
\hfill

%  \textbf{Keynotes}
%\underline{\textbf{ {Keynotes}}}
%\begin{itemize}
%\item


%(This is a conference organized by RSS, solely for presenting and discussing my paper ``Large covariance estimation by thresholding principal orthogonal complements")
%\end{itemize}

%  \textbf{Seminars and Conferences}
%\underline{\textbf{ {Seminars and Conferences}}}
\begin{itemize}
	
	\item The uncertainty of machine learning forecast in asset pricing
	\hfill\\ 
	(2025) \textit{UC Riverside}\\
	(2025)  HKUST IAS-SBM Joint Workshop on Financial Econometrics in the Big Data Era 

\item Does noise hurt economic forecasts ? 
\hfill\\
(2025) \textit{Montreal, UC Riverside, Rutgers, Yale, Philly Fed}  
\hfill\\
(2024) \textit{Duke, McMaster,  UIowa, Philly Fed}  

\item Robust market index forecast using deep learning
\hfill\\
(2023) NBER time series conference, Montreal\\
(2023) Midwest econometric group meeting, Cleveland 



\item Structural deep learning  for  conditional asset pricing models
\hfill\\
(2021-22) \textit{Northwestern, Syracuse, Univ Washington, Virginia Commonwealth, Georgia State}
\\
 (2022) SFS Cavalcade

\item Deep learning inference for semi-parametric conditional moment models
\hfill\\
(2022) \textit{Harvard } \\
(2020) Online Seminar on Selective Inference

  
  \item Fast inference for quantile regressions with tens of millions of observations
  \hfill\\
  (2022-2023) \textit{Virginia Tech, Georgetown, Singapore Management Univ, Albany}  
  
  
 
 
\item Inference for heterogeneous effects using low rank estimation
\hfill\\
(2019-23) \textit{Pittsburgh, Tsinghua, CUHK-SZ, Rochester,  Rutgers, Syracuse, Duke, UPenn, Federal Reserve Bank in Philadelphia}\\
(2019)  33rd New England Statistics Symposium,  Hartford

 
\item Uniform inference for conditional factor models with instrumental and idiosyncratic betas \hfill\\
(2018) \textit{Yale } \\
(2018) California econometrics meeting. CA
 

\item Learning latent factors via diversified projections with applications 
\hfill\\
(2019) Econometric Society Asian Meeting, Xiamen


\item Thousands of alpha tests
\hfill\\
(2019) Sofie, Shanghai


\item Factor-driven two-regime regression \hfill\\
(2018) \textit{UNC, Northwestern} 

\item High dimensional sparse modeling in financial econometrics \hfill\\
(2016) \textit{Emory, Boston University} 


\item The factor-Lasso and k-step bootstrap   for inference in economic applications \hfill\\
   (2016)  \textit{Stevens Institute of Technology, University of Toronto}
   




  \item A lava attack for sparse and dense signals \hfill\\
     (2016) Midwest Econometrics Group, Urbana-Champaign \\
   (2015) Economic and Econometric Applications of Big Data, Cambridge, UK
   
   
  \item Semiparametric Bayesian partially identified models \hfill\\
(2014)   ISBIS meeting, Durham\\
(2014) Econometric Society winter meeting, Philadelphia\\
(2013)   Oberwolfach workshop on partial identification.\\
(2013) \textit{UIUC}

  \item Efficient estimation of approximate factor models \hfill\\
(2013) Joint Statistical Meetings, Montreal\\
(2013-14)  \textit{MIT; George Washington;  Georgetown}


  \item Power enhancement test of high dimensional CAPM models \hfill\\
   (2014) Midwest Econometrics Group, Iowa City\\
      (2014) Econometric Society summer meeting, Minneapolis\\
  (2013) Stevanovich Center for Financial Mathematics,  University of Chicago \\
  (2013)   Midwest Economics Group, Columbus




 \item High dimensional covariance matrix estimation in approximate factor models \hfill\\
  (2012) Midwest Econometrics Group, Lexington, Kentucky\\
  (2011)   \textit{ Cornell}\\
  (2011)  3rd Humboldt-Princeton biennial joint conference, Berlin



\item Ultra high dimensional variable selection with endogenous variables  \hfill\\
(2012)  \textit{Princeton University}\\
(2011) Meetings of the Midwest Econometrics Group, Chicago  




\item Bayesian analysis in moment inequality models \hfill\\
(2010) Econometric Society World Congress, Shanghai\\
(2010)   \textit{Tilburg University}



\end{itemize}

\textbf{Keynote}



  (2013) \textit{Large covariance estimation by thresholding principal orthogonal complements}


 Royal Statistical Society Research Section  \\

%\textbf{Invited Discussant}
%\underline{\textbf{Invited Discussant} }

%(Sep 2011) \textit{Testing High Dimensional CAPM Model}

%Seventh Cambridge-Princeton Conference, Princeton University Bendheim Center for Finance





\section*{TEACHING}
\hrule
\hfill


%\textbf{Instructor }
\begin{itemize}
\item Rutgers University, 2016-Present\\
ECON 322:  Introduction to Econometrics\\
ECON 424:  Machine Learning and Data Analytics\\
ECON 606: Advanced Economic Statistics\\
ECON 706: Advanced Bayesian Inference


\item University of Maryland at College Park, 2012-2016\\
STAT 401: Introduction to Probability and Statistics II \\
  STAT 440: Sampling Theory\\
  STAT 750: Multivariate Analysis\\
 Research Interactive Teams: High-dimensional statistics
\item
Northwestern University, 2010\\
STAT 202: Introduction to Statistics
\end{itemize}






%Developed syllabus, lectured three classes a week, created exams and gave grades.

%\textbf{Teaching Assistant}

% Northwestern University, 2006-2009\\
 %STAT 420-2: Statistical Theory and Methodology\\
%STAT 365: Introduction to Financial Statistics\\
%STAT 351: Design and Analysis of Experiments\\
%STAT 465: Statistical methods in Bioinformatics and computational biology





  \section*{  SERVICE AND OUTREACH}
\hrule
\hfill
\begin{itemize}

\item Editorial Services 

Associate Editor of JASA:  2023-Present 


Associate Editor of Journal of Econometrics:  2020-2024




Associate Editor of JBES:  2017-2021

\item Econometrics Faculty Search Committee Chair, Rutgers 2024-2025

\item Program Committee and Panel

(2016)   9th Annual Conference of The Society for Financial Econometrics (SoFiE)

(2016) National Science Foundation (NSF)  panelist

\item External Reviewing for Research Grants Proposals

(2015-2019)  Research Grants Council (RGC) of Hong Kong

(2015)  Natural Sciences and Engineering Research Council of Canada  (NSERC)


\item Reviewing Activities for Journals and Presses:



  Econometrica, Journal of Econometrics, Review of Financial Studies, Journal of Empirical Finance, Annals of Statistics, Biometrika,  Electronic Journal of Statistics, The Econometrics Journal, Mathematical Finance, JASA, Management Science, Statistica Sinica,   Journal of Computational and Graphical Statistics, Econometric Theory, Journal of Multivariate Analysis, JRSS-B, Psychometrika, Review of Economic Studies, Journal of Statistical Planning and Inference, Journal of Business and Economic Statistics, Statistics and Computing, Statistics and Probability Letters, Journal of Statistical Theory and Practice, Journal of Nonparametric Statistics

\item University Committees

 (2023-2024) Faculty Appointment and Promotion committee, Rutgers University

 
 (2017-present) Policy/Admission/ executive committee, Department of Economics, Rutgers University

 (2015) Policy committee, Department of Math, University of Maryland


 %(2014) participated in the modular model project ``Scientific Computation and Quantitative Exploration of Data".


\end{itemize}




%\section*{PENDING GRANT SUBMISSIONS}
%\hrule
%\hfill

%2015 NSF proposal: Bayesian set inference: theory and applications. submitted to DMS division, pending.





\section*{STUDENTS ADVISING}
\hrule
\hfill


\begin{itemize}
\item As PhD committee chair:

Sung Hoon Choi (2021, tenure track position at University of Connecticut), 

Junjun Choi (2022, postdoc at Columbia University)

Hyukjun Kwon (2024, postdoc at Princeton University)

 
 \textit{Before 2021:}  Jaeheon Jung, Wanjun Li (2020), Junjun Choi (2022),    all from Rutgers.   
 

\item  As committee member: 

\textit{Ph.D. students:}

(2018-Present)  Sungkyung Lee, Weiqi Xiong, Mingmian Cheng, Jessica Schlossberg (Rutgers)



(2013-2015)  Lujia Su and Qi Liu (all from UMaryland)

\end{itemize}



\section*{PROFESSIONAL MEMBERSHIPS}
\hrule
\hfill

Econometric Society, 2009-Present\\
American Finance Association, 2018-Present\\
American Statistical Association, 2010-2013\\
International Indian Statistical Association, 2013-2015\\
Institute of Mathematical Statistics, 2010-2011\\


\begin{comment}
\newpage
\section*{REFERENCES}
\hrule
\hfill
\vspace{2em}

\begin{minipage}{0.45\linewidth}
 {\bf Wenxin Jiang}\\
Professor of Statistics\\
Northwestern University\\
2006 Sheridan Road\\
Evanston, IL 60208\\
Tel: (847) 491 5081\\
Email: wjiang@northwestern.edu
\end{minipage}
\begin{minipage}{0.45\linewidth}
 {\bf Jianqing Fan}\\
Frederick L. Moore '18 Professor of Finance\\
 Professor of Statistics\\
Princeton University\\
205 Sherrerd Hall\\
Princeton, NJ 08544\\
Tel: (609) 258-9863\\
Email: jqfan@princeton.edu
\end{minipage}


\vspace{2em}


\begin{minipage}{0.45\linewidth}
{\bf Elie Tamer}\\
Breen Family Professor of Economics\\
Northwestern University\\
Andersen Hall 342\\
2001  Sheridan Road\\
Evanston, IL 60208\\
Tel: (847) 491-8218\\
Email: tamer@northwestern.edu
\end{minipage}
\begin{minipage}{0.45\linewidth}
{\bf Bruce Spencer}\\
Professor of Statistics\\
Northwestern University\\
Andersen Hall 342\\
2006 Sheridan Road\\
Evanston, IL 60208\\
Tel: (847) 491-5810 \\
Email: bspencer@northwestern.edu
\end{minipage}
\vspace{2em}
%\begin{minipage}{0.45\linewidth}
%{\bf Larry V. Hedges}\\
%Board of Trustees Professor of Statistics and Social Policy\\
%Northwestern University\\
%2040  Sheridan Road\\
%Evanston, IL 60208\\
%Tel: (847) 491-8899\\
%Email: l-hedges@northwestern.edu
%\end{minipage}
\vspace{1em}

\end{comment}

%\bigskip

\end{document} 